Forschungsprojekt

### 2020-10-14 documentation/presentation/main.tex
:-)

\begin{document}
% Ich weiß, dass es die Beamer-Klasse gibt.
% Lasst mich doch alle in Ruhe!
% Die hier hatte ich noch rumliegen, das muss jetzt reichen.
\section{Introduction}
\begin{itemize}
	\item 
In the past years several graph processing systems emerged.
Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.
\item Comparison of non-uniform memory access (NUMA) aware systems and Giraph in their performance
\begin{itemize}
	\item on different graphs (real world and synthetic)
\item and different algorithms (SSSP, BFS, PR)
\end{itemize}
\end{itemize}

\clearpage
\section{Overview}

@@

\begin{multicols}{2}
\begin{description}
	\item[$\color{Galois}\blacksquare$ Galois] is a general purpose library designed for parallel programming
	\begin{itemize}
		\item Version 6.0 from 29\textsuperscript{th} June 2020 used 
	\end{itemize}
	\item[$\color{Gemini}\blacksquare$ Gemini] uses a distributed message-based approach from scratch
	\begin{itemize}
		\item Version from 2\textsuperscript{nd} November 2016 used
		\item Version contains bugs that had to be fixed 
	\end{itemize}
	\item[$\color{Giraph}\blacksquare$ Giraph] is built on Apache Hadoop, a large scale data processing infrastructure
	\begin{itemize}
		\item Version 1.3 from 8\textsuperscript{th} May 2020 used
		\item BFS is not natively supported 
	\end{itemize}
	\item[$\color{Ligra}\blacksquare$ Ligra] dynamically switches between push and pull style
	\begin{itemize}
		\item Version from 14\textsuperscript{th} August 2019
	\end{itemize}
	\item[$\color{Polymer}\blacksquare$ Polymer] optimizes data layout and memory access strategies
	\begin{itemize}
		\item Version from 28\textsuperscript{th} August 2018
	\end{itemize}
\end{description}
\end{multicols}

\section{Evaluation}
\begin{multicols}{2}
\noindent 5 Machines, with
\begin{itemize}
	\item 96 cores, of which 48 virtual
	\item 256 GB of RAM each, one machine only 128 GB
	\item Ubuntu 18.04.2 LTS
\end{itemize}
\noindent Measurements:
\begin{itemize}
	\item \textbf{execution time}: time from start to finish of the console command
	\item \textbf{calculation time}: time the framework actually executed the algorithm
	\item \textbf{overhead}: time difference between execution time and calculation time \newline (time to read the input graph, initialization, etc.)
\end{itemize}

@@

\begin{center}
	\renewcommand{\arraystretch}{1.2}%
	\begin{tabular}{crr}
		\hline
		\bf{Graph}&\# Vertices (M)&\# Edges (M)\\\hline
		flickr&    		0.1&  2\\
		orkut&          3&    117\\
		wikipedia&      12&   378\\
		twitter&     	52&   1963\\
		rMat27&         63&   2147\\
		friendster&     68&   2586\\
		rMat28&         121&  4294\\
		\hline
	\end{tabular}
\end{center}

each test case (graph, framework, algorithm) was run 10 times
\end{multicols}

\clearpage
\begin{multicols}{2}
\section{Production Case}
\begin{itemize}
	\item running system, that performs multiple calculations on a single graph
	\item without the need of reloading graph data with every calculation
	\item short calculation times should be preferred because the overhead time is only spent once on startup and amortizes quickly
\end{itemize}

\columnbreak
\section{Research Case}
\begin{itemize}
	\item individual calculations on a graph, i.e. for each calculation, the graph has to be loaded
	\item the algorithm can change frequently
	\item requiring the framework to be relatively fast on different algorithms
	\item overall small execution times and small overhead are preferred
\end{itemize}
\end{multicols}

@@

\section{Galois With Hugepages}
\begin{multicols}{2}

\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}r}
		\toprule
		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/\\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2 \\
		& orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5 \\
		& wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1 \\
		& twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1 \\
		& rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4 \\
		& friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5 \\
		& rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1 \\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR Pull}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2 \\
		& orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6 \\
		& wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4 \\
		& twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3 \\
		& rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1 \\
		& friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1 \\
		& rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4 \\
		\bottomrule
\end{tabular}

	\includegraphics[width=0.7\linewidth]{../../plots/singleNodeSSSPGaloisHPThreads.png}
	SSSP

	\includegraphics[width=0.7\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
	PR Pull
\end{multicols}

>>>>

\begin{document}
% Ich weiß, dass es die Beamer-Klasse gibt.
% Lasst mich doch alle in Ruhe!
% Die hier hatte ich noch rumliegen, das muss jetzt reichen.
\section{Introduction}
\begin{center}
	\begin{minipage}{0.6\linewidth}
		\centering
		Main Goal: \itshape  Comparison of five graph processing systems in their performance on different graphs and algorithms.
	\end{minipage}
\end{center}

\begin{enumerate}
	\item Preliminaries
	\begin{itemize}
	\item Basics
	\item Computation Styles
	\item Hugepages
	\end{itemize}
	\item Frameworks
	\item Evaluation
	\begin{itemize}
	\item Research vs. Production Case
	\item Results for those Cases
	\item Impact of Hugepages on Galois
	\end{itemize}
	\item Conclusion
\end{enumerate}

% In the past years several graph processing systems emerged.
% Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.

@@

\begin{multicols}{2}
\begin{description}
	\item[$\color{Galois}\blacksquare$ Galois] is a general purpose library designed for parallel programming
	\begin{itemize}
		\item Version 6.0 from 29\textsuperscript{th} June 2020 used 
	\end{itemize}
	\item[$\color{Gemini}\blacksquare$ Gemini] uses a distributed message-based approach from scratch
	\begin{itemize}
		\item Version from 2\textsuperscript{nd} November 2016 used
		\item Version contains bugs that had to be fixed 
	\end{itemize}

@@

	\item[$\color{Giraph}\blacksquare$ Giraph] is built on Apache Hadoop, a large scale data processing infrastructure
	\begin{itemize}
		\item Version 1.3 from 8\textsuperscript{th} May 2020 used
		\item BFS is not natively supported 
		\item state-of-the-art, but not NUMA-aware
	\end{itemize}
	\item[$\color{Ligra}\blacksquare$ Ligra] dynamically switches between push and pull style
	\begin{itemize}
		\item Version from 14\textsuperscript{th} August 2019
	\end{itemize}
	\item[$\color{Polymer}\blacksquare$ Polymer] optimizes data layout and memory access strategies
	\begin{itemize}
		\item Version from 28\textsuperscript{th} August 2018
	\end{itemize}
\end{description}
\end{multicols}

\section{Evaluation}
\begin{multicols}{2}
\noindent Machines: vsflash1-5, 
\begin{itemize}
	\item 96 cores, of which 48 virtual
	\item 256 GB of RAM each\footnote{\sffamily one machine only 128 GB}
	\item Ubuntu 18.04.2 LTS
\end{itemize}
\noindent Measurements:
\begin{itemize}
	\item \textbf{execution time}: time from start to finish of the console command
	\item \textbf{calculation time}: time the framework actually executed the algorithm
	%\item \textbf{overhead}: time difference between execution time and calculation time \newline (time to read the input graph, initialization, etc.) -- brauchen wir das überhaupt?
	\item executed each test case 10 times
\end{itemize}

\begin{center}
	\includegraphics[width=\linewidth]{graphsize.png}
\end{center}

\end{multicols}

\clearpage
\begin{multicols}{2}
\section{Production Case}
\begin{itemize}
	\item running system: multiple calculations on a single graph
	\item graph data stays loaded between calculations
	\item[$\rightarrow$] short calculation times should be preferred
\end{itemize}

\columnbreak
\section{Research Case}
\begin{itemize}
	\item individual calculation cases: possibly new graph for each calculation
	\item frequently changing algorithm
	\item[$\rightarrow$] framework should be relatively fast on different algorithms
	\item[$\rightarrow$] overall small execution times should be preferred
\end{itemize}
\end{multicols}

@@

\section{Galois With Hugepages}
\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}r}

		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/\\
		\midrule
\multirow{7}{0.5ex}{\rotatebox{90}{\bf SSSP}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		& orkut & 0.10 & \bf 0.02 & 0.8 & \bf 0.5\\
		& wikipedia & 0.38 & \bf 0.11 & 1.8 & \bf 1.1\\
		& twitter & 2.47 & \bf 0.94 & 10.8 & \bf 5.1\\
		& rMat27 & 4.50 & \bf 1.39 & 16.0 & \bf 6.4\\
		& friendster & 4.70 & \bf 1.78 & 14.4 & \bf 7.5\\
		& rMat28 & 9.77 & \bf 3.34 & 27.8 & \bf 13.1\\
\end{tabular}
\includegraphics[width=8cm]{../../plots/singleNodeSSSPGaloisThreads.png}
\includegraphics[width=8cm]{../../plots/singleNodeSSSPGaloisHPThreads.png}

\section{Galois With Hugepages}
\begin{tabular}{ccr@{\tabskip 2 \tabcolsep}rr@{\tabskip 2 \tabcolsep}rc}
		&&\multicolumn{2}{c}{\bf Calc Time (s)}&\multicolumn{2}{c}{\bf Exec Time (s)}\\
		\cmidrule{3-4}\cmidrule{5-6}
		&\bf Graph&w/o&w/&w/o&w/\\
		\midrule
	\multirow{7}{0.5ex}{\rotatebox{90}{\bf PR Pull}}
		& flickr & 0.01 & \bf 0.01 & 0.3 & \bf 0.2\\
		& orkut & 0.06 & \bf 0.02 & 0.7 & \bf 0.6\\
		& wikipedia & 0.17 & \bf 0.03 & 1.7 & \bf 1.4\\
		& twitter & 0.77 & \bf 0.11 & \bf 8.7 & 9.3\\
		& rMat27 & 0.65 & \bf 0.13 & 19.2 & \bf 8.1\\
		& friendster & 1.01 & \bf 0.14 & 20.4 & \bf 13.1\\
		& rMat28 & 1.15 & \bf 0.24 & 46.0 & \bf 16.4\\
\end{tabular}
\includegraphics[width=0.5\linewidth]{../../plots/singleNodePRPullGaloisThreads.png}
\includegraphics[width=0.5\linewidth]{../../plots/singleNodePRPullGaloisHPThreads.png}
